---
title: "Metaanalysis in R"
author: "Leyla Ellazova"
date: today
format:  
  html:
    theme: lumen
    toc: true
    toc_float: true
title-block-banner: true
execute:
  echo: fenced
editor_options:
  chunk_output_type: console
---

```{r}
#| label = "setup",
#| include = FALSE
library(meta)
library(metafor)
library(dplyr)
library(ggplot2)
#setwd("")
```

# ASSIGNMENT 

1) Import the data from the `data\metaanalysis_data.xlsx` file. The data come from the meta-analysis study: [Todd et al., 2017 - Sex differences in children's toy preferences: A systematic review, meta‐regression, and meta‐analysis](https://onlinelibrary.wiley.com/doi/full/10.1002/icd.2064)

The study looks at various studies of children choosing what kind of toys they play with (stereotypically 'boy-toys' or stereotypically 'girl-toys'). Mean times (in seconds) of playing are recorded, along with sample sizes and standard errors (for boys playing with each kind of toys and for girls playing with each kind of toys).

There's also information about the studies (e.g. year) and a bit about quality.

Here's authors' descriptions to the data:

> Neutral toys (1 = neutral toys included; 2 = neutral toys not included); Parent present (1 = absent; 2 = minimal interaction; 3 = moderate or full interaction); Setting = location of study (1 = home; 2 = laboratory; 3 = nursery); Country = gender inequality index, a measure of how gender egalitarian the country was at the time the study took place.

> Note. Quality is assessed using Newcastle–Ottawa Quality Assessment Scale criteria adapted for this study. A star indicates that the study fulfilled this criterion; an X indicates that the
study did not fulfil this criterion. 
Case definition adequate: clear justification for the gendered nature of a toy, for example, based on research. 
Representativeness of cases: recruitment of consecutive participants. 
Selection of controls: whether boys and girls were comparable in terms of social background.
Parental opinion: whether parents' views on gender were measured.
Comparability of both groups: the toys were comparable (in size, shape, etc.) and if the boys and girls were comparable in age. 
Ascertainment of behaviour: Play behaviour was clearly defined. 
Same ascertainment method for both groups: The measurement of the outcome (time spent playing with toy) was clearly defined. 
Nonresponse rate: whether either nonuptake or dropout rates reported.

2) Experiment using what you've learned:

a) combine the effects
b) create a funnel plot (what do you see?)
c) check if methods / quality affect the results
d) does author gender affect it?

# Loading dataset first 

```{r , echo = FALSE}
data <- readxl::read_excel("data/metaanalysis_data.xlsx")
head(data)
```

## Repeat what we leaarned in the class from case 2 use same codes

```{r , echo = FALSE}
m.raw <- metacont(n.e = N_boys,
                  mean.e = Mean_boys_play_male,
                  sd.e = SD_boys_play_male,
                  n.c = N_girls,
                  mean.c = Mean_girls_play_female,
                  sd.c = SD_girls_play_female,
                  data = data,
                  studlab = paste(Study),
                  fixed = TRUE,
                  random = TRUE,
)
m.raw
```

Now as in the class we will use `meta`package this is very simple and useful package. We just put our results into the `forest()` function:

### First observation :
```{r , echo = FALSE}
m.raw %>% forest(sortvar = TE, fontsize = 4.5, squaresize = 0.5, col.square = 'blue')
```


### Second observation :
```{r , echo = FALSE}
m.raw %>% metareg(`Parental opinion` + `Representativeness of cases`)
```


### Third observation :
```{r , echo = FALSE}
m.raw %>% metareg(`Female authors` + `Male authors`)
```

ALl in all, the final opinion after looking at all 3 observation points is that observation from first part are mostly centered, and evn those that look like not centered are actually very close to center, which means that all of them have very small SE(standard errors). When conitueing with second point, we can see that Parental opinion has significan effect. When swtching to third observation we can clearly say that gender does not have any effect on results.


# Funnel plot 
```{r , echo = FALSE}
m.raw %>% funnel()
```

### Also in this part we can clearly see that the results are vry similar to the first plot, meaning that majority of them are around the center. Now we can also add some more features to our plot :

```{r, echo = FALSE}
contour_levels <- c(0.90, 0.95, 0.99)
contour_colors <- c("darkblue", "blue", "lightblue")
funnel(m.raw, contour = contour_levels, col.contour = contour_colors)
legend("topright", c("p < 0.10", "p < 0.05", "p < 0.01"), bty = "n", fill = contour_colors)
```
### And even here we see same story. 